---
title: "Research Wikipedia Radar"
author: "Kevin Lu"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  flexdashboard::flex_dashboard: 
    theme: cerulean 
    orientation: columns 
    vertical_layout: scroll 
---

```{r, include = FALSE}
source("./R/rsearch/02-research-wikipedia.R")
```

Price vs Views Level {data-icon="fa-line-chart"}
=========================================

Price vs Views Column A {.tabset .tabset-fade}
-------------------------------------

### Top 20

```{r, fig.width = 12, fig.height = 6}
plot_list_a[["Top 20"]]
```


### en

```{r, fig.width = 12, fig.height = 6}
plot_list_a[["en.wikipedia"]]
```

### ru

```{r, fig.width = 12, fig.height = 6}
plot_list_a[["ru.wikipedia"]]
```

### de

```{r, fig.width = 12, fig.height = 6}
plot_list_a[["de.wikipedia"]]
```

### es

```{r, fig.width = 12, fig.height = 6}
plot_list_a[["es.wikipedia"]]
```

### zh

```{r, fig.width = 12, fig.height = 6}
plot_list_a[["zh.wikipedia"]]
```

### ja

```{r, fig.width = 12, fig.height = 6}
plot_list_a[["ja.wikipedia"]]
```

### fr

```{r, fig.width = 12, fig.height = 6}
plot_list_a[["fr.wikipedia"]]
```

### it

```{r, fig.width = 12, fig.height = 6}
plot_list_a[["it.wikipedia"]]
```

### pt

```{r, fig.width = 12, fig.height = 6}
plot_list_a[["pt.wikipedia"]]
```

### vi

```{r, fig.width = 12, fig.height = 6}
plot_list_a[["vi.wikipedia"]]
```

### pl

```{r, fig.width = 12, fig.height = 6}
plot_list_a[["pl.wikipedia"]]
```

### ar

```{r, fig.width = 12, fig.height = 6}
plot_list_a[["ar.wikipedia"]]
```

### nl

```{r, fig.width = 12, fig.height = 6}
plot_list_a[["nl.wikipedia"]]
```

### ko

```{r, fig.width = 12, fig.height = 6}
plot_list_a[["ko.wikipedia"]]
```

### cs

```{r, fig.width = 12, fig.height = 6}
plot_list_a[["cs.wikipedia"]]
```

### id

```{r, fig.width = 12, fig.height = 6}
plot_list_a[["id.wikipedia"]]
```

### tr

```{r, fig.width = 12, fig.height = 6}
plot_list_a[["tr.wikipedia"]]
```

### uk

```{r, fig.width = 12, fig.height = 6}
plot_list_a[["uk.wikipedia"]]
```

### hu

```{r, fig.width = 12, fig.height = 6}
plot_list_a[["hu.wikipedia"]]
```

### sv

```{r, fig.width = 12, fig.height = 6}
plot_list_a[["sv.wikipedia"]]
```

Price vs Views Column B
-------------------------------------

### 

Last updated on **`r Sys.Date()`**. 

This plot displays the BTCUSD exchange rate along with the number of daily pageviews of the bitcoin Wikipedia page in various 
languages. Using Wikipedia page views can serve as a measure of interest from new and potential investors of bitcoin because 
investors are likely to begin their research by reading the Wikipedia page. This indicator can be engineered into a feature for 
use in momentum-type models and is consistent with the theory that there is persistence in performance due to the long series 
of steps for a new investor to begin accumulating bitcoin. 

The Top 20 tab represents an aggregation of the page views from the top 20 languages. Each language referred to as a project in 
the Wikipedia API. The subsequent tabs represent page views from individual projects. 

Data Sources:  
- Bitcoin exchange rate data obtained from BitStamp via Quandl. 
- Wikipedia page view data obtained from https://tools.wmflabs.org/pageviews/. 

Price vs Views Change {data-icon="fa-line-chart"}
=========================================

Price vs Views Change Column A {.tabset .tabset-fade}
-------------------------------------

### Top 20

```{r, fig.width = 12, fig.height = 8}
plot_list_b[["Top 20"]]
```


### en

```{r, fig.width = 12, fig.height = 8}
plot_list_b[["en.wikipedia"]]
```

### ru

```{r, fig.width = 12, fig.height = 8}
plot_list_b[["ru.wikipedia"]]
```

### de

```{r, fig.width = 12, fig.height = 8}
plot_list_b[["de.wikipedia"]]
```

### es

```{r, fig.width = 12, fig.height = 8}
plot_list_b[["es.wikipedia"]]
```

### zh

```{r, fig.width = 12, fig.height = 8}
plot_list_b[["zh.wikipedia"]]
```

### ja

```{r, fig.width = 12, fig.height = 8}
plot_list_b[["ja.wikipedia"]]
```

### fr

```{r, fig.width = 12, fig.height = 8}
plot_list_b[["fr.wikipedia"]]
```

### it

```{r, fig.width = 12, fig.height = 8}
plot_list_b[["it.wikipedia"]]
```

### pt

```{r, fig.width = 12, fig.height = 8}
plot_list_b[["pt.wikipedia"]]
```

### vi

```{r, fig.width = 12, fig.height = 8}
plot_list_b[["vi.wikipedia"]]
```

### pl

```{r, fig.width = 12, fig.height = 8}
plot_list_b[["pl.wikipedia"]]
```

### ar

```{r, fig.width = 12, fig.height = 8}
plot_list_b[["ar.wikipedia"]]
```

### nl

```{r, fig.width = 12, fig.height = 8}
plot_list_b[["nl.wikipedia"]]
```

### ko

```{r, fig.width = 12, fig.height = 8}
plot_list_b[["ko.wikipedia"]]
```

### cs

```{r, fig.width = 12, fig.height = 8}
plot_list_b[["cs.wikipedia"]]
```

### id

```{r, fig.width = 12, fig.height = 8}
plot_list_b[["id.wikipedia"]]
```

### tr

```{r, fig.width = 12, fig.height = 8}
plot_list_b[["tr.wikipedia"]]
```

### uk

```{r, fig.width = 12, fig.height = 8}
plot_list_b[["uk.wikipedia"]]
```

### hu

```{r, fig.width = 12, fig.height = 8}
plot_list_b[["hu.wikipedia"]]
```

### sv

```{r, fig.width = 12, fig.height = 8}
plot_list_b[["sv.wikipedia"]]
```

Price vs Views Change Column B
-------------------------------------

### 

This plot displays the BTCUSD exchange rate along with the 7-day percent change in page views. A 7-day percent change 
was used to determine when there is a large influx of new readers by removing the trend and correcting for the weekly 
seasonality in the series. Other approaches using moving averages or rolling z-scores did not produce good results. 
Using a 7-day percent change accurately identifies the peaks in page views and is consistent with visual identification 
of peaks. 

Price vs Views Signal {data-icon="fa-line-chart"}
=========================================

Price vs Views Signal Column A {.tabset .tabset-fade}
-------------------------------------

### Top 20

```{r, fig.width = 12, fig.height = 6}
plot_list_c[["Top 20"]]
```


### en

```{r, fig.width = 12, fig.height = 6}
plot_list_c[["en.wikipedia"]]
```

### ru

```{r, fig.width = 12, fig.height = 6}
plot_list_c[["ru.wikipedia"]]
```

### de

```{r, fig.width = 12, fig.height = 6}
plot_list_c[["de.wikipedia"]]
```

### es

```{r, fig.width = 12, fig.height = 6}
plot_list_c[["es.wikipedia"]]
```

### zh

```{r, fig.width = 12, fig.height = 6}
plot_list_c[["zh.wikipedia"]]
```

### ja

```{r, fig.width = 12, fig.height = 6}
plot_list_c[["ja.wikipedia"]]
```

### fr

```{r, fig.width = 12, fig.height = 6}
plot_list_c[["fr.wikipedia"]]
```

### it

```{r, fig.width = 12, fig.height = 6}
plot_list_c[["it.wikipedia"]]
```

### pt

```{r, fig.width = 12, fig.height = 6}
plot_list_c[["pt.wikipedia"]]
```

### vi

```{r, fig.width = 12, fig.height = 6}
plot_list_c[["vi.wikipedia"]]
```

### pl

```{r, fig.width = 12, fig.height = 6}
plot_list_c[["pl.wikipedia"]]
```

### ar

```{r, fig.width = 12, fig.height = 6}
plot_list_c[["ar.wikipedia"]]
```

### nl

```{r, fig.width = 12, fig.height = 6}
plot_list_c[["nl.wikipedia"]]
```

### ko

```{r, fig.width = 12, fig.height = 6}
plot_list_c[["ko.wikipedia"]]
```

### cs

```{r, fig.width = 12, fig.height = 6}
plot_list_c[["cs.wikipedia"]]
```

### id

```{r, fig.width = 12, fig.height = 6}
plot_list_c[["id.wikipedia"]]
```

### tr

```{r, fig.width = 12, fig.height = 6}
plot_list_c[["tr.wikipedia"]]
```

### uk

```{r, fig.width = 12, fig.height = 6}
plot_list_c[["uk.wikipedia"]]
```

### hu

```{r, fig.width = 12, fig.height = 6}
plot_list_c[["hu.wikipedia"]]
```

### sv

```{r, fig.width = 12, fig.height = 6}
plot_list_c[["sv.wikipedia"]]
```

Price vs Views Signal Column B
-------------------------------------

### 

This plot displays the BTCUSD exchange rate with 7-day percent change overlayed as a color and size gradient. 
Large bright red dots indicate days where there is a very large increase in page views. Medium gray dots indicate 
days where there is a moderate increase in page views. Small blue dots indicate days where the the page views are 
stable. 

Price vs Views Threshold {data-icon="fa-line-chart"}
=========================================

Price vs Views Threshold Column A {.tabset .tabset-fade}
-------------------------------------

### Top 20

```{r, fig.width = 12, fig.height = 6}
plot_list_d[["Top 20"]]
```


### en

```{r, fig.width = 12, fig.height = 6}
plot_list_d[["en.wikipedia"]]
```

### ru

```{r, fig.width = 12, fig.height = 6}
plot_list_d[["ru.wikipedia"]]
```

### de

```{r, fig.width = 12, fig.height = 6}
plot_list_d[["de.wikipedia"]]
```

### es

```{r, fig.width = 12, fig.height = 6}
plot_list_d[["es.wikipedia"]]
```

### zh

```{r, fig.width = 12, fig.height = 6}
plot_list_d[["zh.wikipedia"]]
```

### ja

```{r, fig.width = 12, fig.height = 6}
plot_list_d[["ja.wikipedia"]]
```

### fr

```{r, fig.width = 12, fig.height = 6}
plot_list_d[["fr.wikipedia"]]
```

### it

```{r, fig.width = 12, fig.height = 6}
plot_list_d[["it.wikipedia"]]
```

### pt

```{r, fig.width = 12, fig.height = 6}
plot_list_d[["pt.wikipedia"]]
```

### vi

```{r, fig.width = 12, fig.height = 6}
plot_list_d[["vi.wikipedia"]]
```

### pl

```{r, fig.width = 12, fig.height = 6}
plot_list_d[["pl.wikipedia"]]
```

### ar

```{r, fig.width = 12, fig.height = 6}
plot_list_d[["ar.wikipedia"]]
```

### nl

```{r, fig.width = 12, fig.height = 6}
plot_list_d[["nl.wikipedia"]]
```

### ko

```{r, fig.width = 12, fig.height = 6}
plot_list_d[["ko.wikipedia"]]
```

### cs

```{r, fig.width = 12, fig.height = 6}
plot_list_d[["cs.wikipedia"]]
```

### id

```{r, fig.width = 12, fig.height = 6}
plot_list_d[["id.wikipedia"]]
```

### tr

```{r, fig.width = 12, fig.height = 6}
plot_list_d[["tr.wikipedia"]]
```

### uk

```{r, fig.width = 12, fig.height = 6}
plot_list_d[["uk.wikipedia"]]
```

### hu

```{r, fig.width = 12, fig.height = 6}
plot_list_d[["hu.wikipedia"]]
```

### sv

```{r, fig.width = 12, fig.height = 6}
plot_list_d[["sv.wikipedia"]]
```

Price vs Views Threshold Column B
-------------------------------------

### 

This plot displays the BTCUSD exchange rate with an illustrative long signal derived from the 7-day 
percent change in page views. Red dots indicate days where the 7-day percent change is greater than 
the 98.5th percentile. Green dots indicate days where the 7-day percent change is greater than the 
99th percentile. The plots suggest that green and red dots precede most of the periods where the price 
increased rapidly.  
